\chapter*{Acknowledgements}

First and foremost I would like to thank my advisor, Dr. Stephen McKean, without whom this thesis would not be possible. I first met Stephen in his topics class on topological modular forms. Aside from fascinating mathematics, I learned two important things: the power of beautiful mathematical storytelling, and the joys of homotopy theory applied to geometry. 
When I reached out to Stephen to ask about a senior thesis project, he suggested the topic of exotic spheres -- one of the great stories of differential topology and homotopy theory. I am very glad I reached out, since this thesis has turned out to be by far my most academically enriching undertaking during my time at Harvard. Stephen's guidance, encouragement, and frequent course corrections have been invaluable throughout the process.

I would also like to express my deep gratitude to Professor Dan Freed, one of the constants in my mathematical journey at Harvard.
Aside from imbuing me with a deep appreciation for geometric perspectives, Professor Freed continually inspires me with his unique skills of exposition. Through a steady stream of seemingly elementary observations, Professor Freed is able to make even the most non-trivial theorem feel canonical, as if you could have discovered it yourself.
This is easier said than done -- one of my most memorable experiences with Professor Freed was our unconventional reading group which involved no reading at all. Instead, we were tasked with independently discovering fundamental results in differential geometry -- an approach that was challenging yet incredibly educational.

Additionally, I would like to thank the many professors of the Harvard math department who have shaped the past four years -- 
Professors Denis Auroux, Barry Mazur, Mike Hopkins, H.T. Yau, Curtis McMullen, Peter Kronheimer, and Cliff Taubes. A special thank-you is owed to Dr. Andy Senger for our many illuminating conversations on algebraic topology and for setting me firmly on a  topological track early on. 

One of the best aspects of the math department has been its students. I am particularly  grateful to my dear friends AJ, Ignasi, Jarell, Leonardo, Zach, and many others with whom I've spent countless late nights working on math. My Harvard experience truly would not have been the same without you.
Of course, I also owe a tremendous amount to my wonderful roommates, Kalman, Ellen, Swati, Mya, and AJ -- especially for their understanding of my frequent disappearances to work on my thesis; to Jane for her emotional support and encouragement; to Nikita and Nick for listening to my mathematical ramblings on our hikes; and to the rest of my amazing friends for keeping me grounded and sane over the past year. 

Last but not least I would like to thank my parents, whose unwavering support has shaped me from the very beginning. Your encouragement, patience, and belief in me have meant the world to me. I hope this thesis brings you some well-deserved \emph{naches} in return.
