\chapter{Constructions}\label{chap:constructions}

\begin{epigraph}{25em}{Lao Tsu}
Existence, by nothing bred, breeds everything.\\
Parent of the universe, it smooths rough edges,\\
Unties hard knots, tempers the sharp sun, \\
lays blowing dust, its image in the well spring never fails. \\
But how was it conceived? -- this image of no other sire.
\end{epigraph}

The focus on this chapter will be on some of the constructions of exotic spheres -- as total spaces of sphere bundles, as the boundary of a ``plumbing'' of disk bundles along a tree, as the ``link'' of an isolated singularity of a holomorphic functions, or as a ``twisted'' gluing of two disks. Using the results of \cref{chap:invariants} it is be possible to compute which elements of $\Theta^n$ these manifolds correspond to.

As with many challenging topics in math, an abundance of examples helps alleviate some of the complexity, and we hope this chapter can do this for exotic spheres.
The basic ingredients for a good exotic sphere construction includes the following:
\begin{enumerate}[(a)]
	\item A general class of non-trivial smooth manifolds which have highly-connected boundary.
	\item A simple criterion for when this boundary is homotopy equivalent to a sphere.
	\item Some geometric structure on the bounding manifold which simplifies the computation of topological invariants.
\end{enumerate}

\input{chapters/constructions/milnor-spheres.tex}
\input{chapters/constructions/plumbing.tex}
\input{chapters/constructions/brieskorn.tex}
\input{chapters/constructions/twisted.tex}
